Energy Injection for Mechanical Systems via Virtual Nonholonomic Constraints

### 2020-03-01 latex/bcc/main.tex
Shorten the abstract
The abstract was over 1 page long, so I cut some stuff out, removed some
newlines, and added a bit of extra detail. It is now exactly one page
long.

%---------- Summary of Ideas ----------%
A \textit{virtual nonholonomic constraint} (VNHC) is a smooth relation 
\[
    h : T^\star \mathcal{Q} \rightarrow \mathbb{R}^{n-1}
\]
between the \(n\) configuration variables \(q \in \mathcal{Q}\) and conjugate of
momenta \(p \in T_q^\star\mathcal{Q}\) of a mechanical system with 
\(n-1\) control inputs.
Enforcing these types of constraints via feedback control provides
time-independent controllers which can inject or remove energy from the system.

@@

For the variable-length pendulum we design and enforce a VNHC which achieves a
time-optimal swingup motion, without tracking a signal over time. 
We then prove that anyone swinging while constrained by this VNHC will gain
enough energy to start rotating completely around the swinging axis.

For the acrobot, we design several VNHCs (modelled from the leg motions of human
gymnasts) which achieve human-like ``giant" motion.
We then apply one of these VNHCs to a real acrobot and, through experiments,
demonstrate the energy-injection properties of the VNHC as the robot kicks its
legs and starts doing backflips on the bar.

>>>>

%---------- Summary of Ideas ----------%
A \textit{virtual nonholonomic constraint} (VNHC) is a smooth relation 
\(
    h : T^\star \mathcal{Q} \rightarrow \mathbb{R}^{n-1}
\) 
between the configuration variables \(q \in \mathcal{Q}\) and conjugate of
momenta \(p \in T_q^\star\mathcal{Q}\) of an \(n\)-degree-of-freedom mechanical
system with \(n-1\) control inputs, such that \(h(q,p) = 0\).
Enforcing these types of constraints via feedback control provides
time-independent controllers which can inject or remove energy from the system.

@@

For the variable-length pendulum we design and enforce a VNHC which achieves a
time-optimal swingup motion, without tracking a signal over time. 
We then prove that any pendulum constrained by this VNHC will gain
enough energy to start rotating completely around the swinging axis.

For the acrobot, we design several VNHCs (modelled from the leg motions of human
gymnasts) which achieve human-like ``giant" motion.
We then apply one of these VNHCs to a real acrobot and, through experiments,
demonstrate the energy-injection properties of the VNHC as the robot kicks its
legs until it begins doing backflips on the bar.
